### 2024-02-18 documentation/thesis/thesis_document.tex
.

A solid basement has been built in this version of the framework, which
contains all the necessary functions and is ready for immediate use.
During development, particular emphasis is placed on comprehensive
documentation to make it easier to get started. Together with examples
for various use cases, a user can quickly evaluate the framework.

However, it should be noted that the framework has already been released
with its first stable version, but extensions and improvements are still
necessary. The stable version distributed via the package registry is
well suited for the intended purpose. All tests and evaluations took
place under normal conditions, especially for the developed hardware
sensors, as the \gls{mrp} library works successfully with the
measurement data.

On the software side, the focus is on integration for the support of
more professional measuring devices. Only in this way is it possible to
evaluate and improve the sensor hardware and quantify the measurement
results.

To summarise, it can be said that a solid software framework has been
created that can be used directly for the intended purpose. It provides
a suitable base for working, but further developments by integrating
professional measurement devices to enable a more comprehensive
evaluation and improvement of the sensor hardware are necessary.

>>>>

With this version of the framework, a solid basis has been created that
contains all the necessary functions to solve various problems in the
acquisition and processing of magnetic fields. Easy-to-assemble
measurement hardware has created an easy-to-use platform for the
characterisation of permanent magnets, for example. An exemplary
characterisation of the magnetic field sensors used allows the possible
areas of application for these to be narrowed down. The framework has
already been published in a first stable version, but extensions and
improvements are still necessary. The stable version is also distributed
via a package registration and can therefore be quickly evaluated by new
users. In addition, further user experience and actual measurements
under real laboratory conditions on \gls{mri} B0 field magnets are still
missing. This is limited by the currently restricted selection of
characterised sensors. The aim for the next revision of the hardware and
software framework is therefore to support additional magnetic field
sensors. The current restriction to purely digital sensor interfaces is
also to be extended to analogue interfaces. This will open up the use of
a wide range of magnetic field sensors. It is also possible to integrate
high-resolution magnetic field probes based onNMR samples, which can
cover measurement errors of less than \emph{10nT} in fields of more than
\emph{1T} \customcite{DBN08}. Another possibility already supported by the
software, but for which hardware development is still necessary, is 2D
arrays of magnetic field sensors to display fields on a
surface\customcite{CP16}. This means that deviations can also be
visualised graphically without physically moving the senso such as in
the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
addition, larger areas or volumes, such as in a large \emph{B0} field,
can be measured more quickly.
